### 2019-03-12 papers/journal/problem.tex
qbf Section 5.1 Done

Second, using constraint solving, where the rules are represented as a constraint over the variables defined in the system.
%
The search problem is to find an assignment of variables that satisfies all the specified constraints.
%
We have used a form of this technique called satisfiability modulo theories (SMT).
%
The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-vectors etc. 
%
%It includes formulas with variables from other domains, including real numbers, integers, and support for various data structures such as lists, arrays, bit vectors.
% is satisfiability of formulas with respect to some background theory.
%
Throughout the paper we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
%The existential condition search problem is represented as a bounded model checking and constraint solving. 
%
%Based upon earlier discussion, we need to answer the following search question among VTSs.
%
Here, we will present both $\fbmc$ and $\fsmt$ search problem for the existential condition.

@@

\subsection{Universal condition}
%Here we will present the QBF.
We will model the search problem for the universal condition as a quantified Boolean formula, and resultant formula will be solved with the help of a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifiers.
%
The QBFs enables potentially more succinct encodings than propositional logic.

%\ankit{This is a dummy template. need a rewrite.} 
\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment to make it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.

>>>>

Second, using constraint solving, where the rules are represented as a constraint over the variables defined in the system.
%
The search problem is to find an assignment of variables that satisfies all the specified constraints.
%
We have used a form of this technique called satisfiability modulo theories (SMT)~\cite{nieuwenhuis2006solving, barrett2018satisfiability}.
%
The SMT is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-vectors etc. 
%
%It includes formulas with variables from other domains, including real numbers, integers, and support for various data structures such as lists, arrays, bit vectors.
% is satisfiability of formulas with respect to some background theory.
%
Throughout the paper we will address these two subcategories as $\fbmc$ and $\fsmt$ search problems.
%The existential condition search problem is represented as a bounded model checking and constraint solving. 
%
%Based upon earlier discussion, we need to answer the following search question among VTSs.
%
Here, we will present both $\fbmc$ and $\fsmt$ search problem for the existential condition.

@@

\subsection{Universal condition}
%Here we will present the QBF.
We will model the search problem for the universal condition as a quantified Boolean formula (QBF)~\cite{buning2009theory, benedetti2008qbf}, and resultant formula will be solved with the help of a QBF solver.
%
The QBF is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifiers.
%
The QBFs enables potentially more succinct encodings than SAT but with a higher complexity class decision problem~\cite{buning2009theory}.

%\ankit{This is a dummy template. need a rewrite.} 
\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
